\documentclass[a4paper,11pt]{article}

\usepackage[a4paper,margin=0.55in]{geometry}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{fontawesome}
\usepackage{mathptmx}

\pagestyle{empty}

\setstretch{0.93}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=10pt, itemsep=0.5pt, topsep=0.4pt}

\titleformat{\section}{\large\bfseries}{}{0em}{}
\titlespacing{\section}{0pt}{4pt}{1.5pt}
\newcommand{\sectionline}{\vspace{-6pt}\noindent\rule{\linewidth}{0.5pt}\vspace{1.5pt}}

\begin{document}

% HEADER
\begin{center}
{\LARGE \textbf{Niranjan C N}}\\[3pt]
\faPhone\ \href{tel:+919108269436}{+91 9108269436} \quad
\faEnvelope\ \href{mailto:cnniranjan72@gmail.com}{cnniranjan72@gmail.com} \quad
\faLinkedinSquare\ \href{https://linkedin.com/in/niranjan-c-n}{linkedin.com/in/niranjan-c-n} \hfill
\faGithub\ \href{https://github.com/cnniranjan72}{github.com/cnniranjan72}
\end{center}
\sectionline

% SUMMARY
\section*{\faBullseye\ Summary}
Computer Science undergraduate and Software Engineer building production-grade full-stack and AI systems across aviation and enterprise platforms. Experienced in RAG pipelines, vector databases, and reinforcement learning systems with strong foundations in scalable system design.

\sectionline

% EDUCATION
\section*{\faGraduationCap\ Education}
\textbf{AMC Engineering College — B.E. Computer Science (CGPA: 8.5)} \hfill \textit{2023 – 2027}

\sectionline

% EXPERIENCE
\section*{\faBriefcase\ Experience}

\textbf{Software Development Engineer, AeroAspire — Hybrid} \hfill \textit{Sep 2025 – Present}
\begin{itemize}
\item Built \textbf{AeroBriefs}, a production aviation weather briefing platform centralizing real-time operational data for pilots and ATC workflows.
\item Developed end-to-end system using \textbf{Flutter, Firebase, Firestore} enabling real-time synchronization and scalable data handling.
\item Delivered features under evolving requirements while ensuring \textbf{aviation-grade reliability} and domain-specific constraints.
\end{itemize}

\textbf{AI Developer, Tribeca Softech — Remote} \hfill \textit{Jan 2026 – Present}
\begin{itemize}
\item Built an \textbf{enterprise-grade RAG query engine} supporting attachment-based queries, streaming responses, and conversational context management. Designed multi-mode interaction system including \textbf{focus mode, global mode, and temporary sessions} with dynamic context handling.
\item Developed a \textbf{modular vectorization engine} for multi-source ingestion (S3, databases) with components like input manager, embedding pipeline, optimizer, observer, and profiling layers.
\item Implemented \textbf{retrieval optimization, reranking, and LLM-based reasoning layers} to improve response relevance and handling of conflicting information.
\item Built scalable backend using \textbf{FastAPI, PostgreSQL (Neon), async workflows} enabling real-time processing and extensible AI system design.
\item Developed \textbf{AI research agents} for LinkedIn profile enrichment using Playwright, Firecrawl, and LLM-driven structured data extraction pipelines.
\end{itemize}
\sectionline

% PROJECTS
\section*{\faFolderOpen\ Projects}

\textbf{CIVITAS — AI Smart City Digital Twin} \hfill
\href{https://github.com/cnniranjan72/civitas}{\faGithub}
\begin{itemize}
\item Built multi-domain reinforcement learning system using \textbf{PPO} with real-time simulation dashboard.
\item Integrated \textbf{LLM-based explainability} for policy reasoning and system behavior insights.
\end{itemize}

\textbf{IntelliMine — Autonomous Landmine Detection} \hfill
\href{https://github.com/cnniranjan72/Autonomous-Landmine-detector}{\faGithub}
\begin{itemize}
\item Developed ML-based detection system achieving \textbf{98.2\% accuracy} using Random Forest and PCA.
\item Built full-stack solution with \textbf{React, Flask, MongoDB} including safe path planning.
\end{itemize}

\textbf{Cortex — RAG-Based AI Assistant} \hfill
\href{https://github.com/cnniranjan72/Cortex-RAG}{\faGithub}
\begin{itemize}
\item Built RAG-based AI assistant supporting \textbf{attachment-based queries} with real-time streaming responses.
\item Implemented document pipeline using \textbf{chunking, embeddings, and Pinecone} for semantic retrieval.
\item Developed ChatGPT-like system using \textbf{React, FastAPI, OpenAI APIs} with function calling and structured outputs.
\end{itemize}
\sectionline

% SKILLS
\section*{\faCode\ Skills}
\textbf{Languages:} C, C++, Java, Python, JavaScript, Typescript, Dart, HTML, CSS \\
\textbf{Frameworks:} React.js, Flutter, FastAPI, Flask, Node.js, Express.js, RAG Pipelines \\
\textbf{Databases:} PostgreSQL, MongoDB, MySQL, Firestore, SQLite, Pinecone \\
\textbf{Tools:} Git, Docker, Linux, Postman, Swagger, Playwright

\sectionline

% ADDITIONAL
\section*{\faInfoCircle\ Additional Information}
\textbf{Certifications:} Full-Stack Web Development Bootcamp, Tata GenAI Data Analytics Simulation, Anthropic - Claude Code in Action, Anthropic - AI Fluency: Framework and Foundations, MongoDB for Students\\
\textbf{Interests:} Tech blogs, open source, micro-projects, cricket \\
\textbf{Languages:} English, Kannada, Hindi, Telugu

\end{document}